### 2022-03-03 Journal1/Response2/Response.tex

%\usepackage{fixltx2e}
\usepackage{amsmath, amssymb, upgreek, amsthm}
\usepackage{graphicx}
\usepackage{tikz}
\geometry{letterpaper, left=20mm, right=20mm, top=20mm, bottom=20mm}
\usetikzlibrary{patterns} % LATEX and plain TEX when using Tik Z
\allowdisplaybreaks
\setlength{\textfloatsep}{2ex}
\usepackage{array}
\usepackage{enumitem}
\setlength{\parindent}{1 em}
\setlength{\parskip}{0.5 em}
\renewcommand{\baselinestretch}{1.25}
\def\dsd{d_\text{SD}}
\def\Rcoop{R_\text{Coop}}
\def\rhd{R_\text{HD}}
\def\rsd{R_\text{SD}}
\def\rsh{R_\text{SH}}
\def\Pcoops{\mathcal{P}^\text{Succ}_\text{Coop}}
\def\dsh{d_\text{SH}}
\def\dhd{d_\text{HD}}
\def\psibar{\overline{\mathcal{P}}^\text{Succ}_{i}}
\def\psbara{\overline{\mathcal{P}}^\text{Succ}_{1}}
\def\psbarb{\overline{\mathcal{P}}^\text{Succ}_{2}}
\def\psbarc{\overline{\mathcal{P}}^\text{Succ}_{3}}
\def\psbard{\overline{\mathcal{P}}^\text{Succ}_{4}}
\def\psbare{\overline{\mathcal{P}}^\text{Succ}_{5}}
\def\Ri{R_{i}}
\def\Ps{\mathcal{P}^\text{Succ}_\text{Direct}}
\def\frk{\mathrm{f}_{r_k}(r)}
\def\Rcoopj{R_\text{coop}^j}
\title{\bf \vspace*{-4ex} Statement of Responses to the Editor and the Reviewers of Paper-TNSM \\[-6ex]}
\date{}

\begin{document}
%\vspace*{-10ex}
%\sloppy
\maketitle
We would like to thank the editor and reviewers for their comments on our manuscript.
We hope that the modifications that we have made to the manuscript, and the responses that we have
provided herein will alleviate the reviewers' concerns. Below, please find our detailed responses to the editor and reviewers' comments and suggestions.
\\ [-3.ex]
% % % % % % % % % % % % % % % Editor % % % % % % % % % % % % % % % % % % % %

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Editor} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent  Comments to the Author} ``The paper has gone through three independent reviews and also checked by myself. The topic is interesting and there are merits. But there are some major concerns on the contribution, the assumption, the model derivation, and the experimental results. We hope the review comments are useful for further improving the quality of the paper. I'd therefore recommend the Resubmission''\\
\hline
\end{longtable}

\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the editor for his comment on our manuscript and giving us the opportunity to resubmit it. We have utilized the comments to improve our paper and eliminate the problems.

@@

%\begin{longtable}{|p{0.975\textwidth}|}
%\hline \hline
%\RaggedRight
%\cellcolor{green!10}
%[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.
%\\
%\hline
%\end{longtable}

% % % % % % % % % % % % % % % Reviewer 1 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 1} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The paper proposes resolving the problem of resource allocation to network slices by using a new algorithm applied to the reformulation of the problem. The results seem promising but the paper has some issues. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for the careful and thorough reading of this manuscript. We hope that the responses provided herein can alleviate the reviewer's concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``First, the structure of the paper makes it somewhat hard to follow and there are some mistakes in the text. A proofread is required before it can be accepted for publication.   ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We have changed the paper's introduction and checked the text entirely according to this comment.

@@

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 2:} ``Although the paper demonstrates its claims, the relaxation of conditions from the original problem formulation is not well justified. It is not clear why the initial formulation of the problem is not feasible and the reformulated makes it feasible while retaining some level of quality of the solutions given. A deeper analysis of both formulations must be presented. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
The problem in (13) is feasible and has feasibility points that are discussed in subsection  IV-B, and we introduce a fast algorithm (i.e., Algorithm 3) for feasibility points. Although the problem is feasible, it is not convex and difficult to solve. Since problem in (13) is mixed-integer nonlinear programming with two integer variables, the PRB assignment, $e$, and the number of VNFs in slice $s$, $M_s$, and the problem is NP-hard. Solving the problem is not trivial. To solve the problem by inspiring Stackelberg, we reformulate the equation in (13g) to reduce one of the variables (i.e., $M_s$) that can be solved after obtaining the rate of UEs. WE notice that $M_s$ is similar to the followers in Stackelberg Competition and power and PRB assignment is similar to leader. So, the new problem has two variables of power and PRB assignment. This new problem is convex by relaxing the binary variable, the PRB assignment, and estimating the lower bounds in (15) because the objective function and constraints of the problem are convex and can be solved by the Lagrangian function. After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs. We made changes in Subsection III-A, accordingly.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} ``Moreover, the baseline and FBDR methods used in the comparison are not well introduced. They are vaguely linked to related work but not as needed. The paper must clarify the relation of the related work and the compared alternatives. The paper must also contextualize the proposal among the related work by comparing their qualities and/or performance.  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
 Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach. The first one is a baseline scheme, which uses random PRB allocation. So, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE. Also, the association of O-RU is carried out based on distance. It means that each UE is assigned to the nearest O-RU. The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
After achieving power and other parameters, the achievable rate will be obtained and the optimal number of VNF is
achieved from Lemma (1). The second one is similar
to the fixed BBU capacity and dynamic resource allocation
(FBDR) algorithm proposed in [18]. In this work, we have services with different QoS that
contain UEs, which is similar to tenants with different QoS
that is introduced in [18]. So, we used an algorithm similar
to FBDR adapted to our conditions for comparison. Instead
of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
To use the FBDR method, we should consider the fixed
BBU capacity. We assume that O-DU and O-CU have fixed
sufficient capacity in our system model. Also, our mid-haul
link (F1 link) has adequate capacity, so there will be no
issue using the FBDR method by separating BBU to O-DU
and O-CU with this assumption. In this method, PRB and power are dynamically allocated. The number of VNFs is
obtained from the simulation. The UEs are associated with the O-RU based on the quality of their channels and the
channel distance instead of using the greedy algorithm 1 (GAA algorithm ) for O-RU assignment. The figures in [18]
show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same
priority area. We will also see that our proposed algorithm performs better than FBDR in the numerical result section.

@@

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 1:} ``In terms of taking the actual delay in the proposed there are some concerns which might be important for some time critical applications especially in the ultra-reliable low latency communications (URLLC) but also for different applications that fall under the enhanced mobile broadband (eMBB) generic service framework. First of all, in the paper the authors only consider processing delay and ignore propagation and transmission delay. Since multiple paths in reality could be utilized the role of the above two components might play an important role. Nevertheless, the authors need to clearly mention why those two components are not considered, saying for example are constant is not a good enough reason to be ignored since as eluded those change based on routing decisions.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Taking propagation and transmission delays into formulations is straightforward, but we avoided that for the sake of better presentation. However, they can be added to the system model easily. In this paper, we focus only on the processing delay to find the optimal number of VNFs, and we consider the other two delays are fixed; In the following, we describe more about these two types of delays.

The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority. Also, the connections of O-DUs to O-CUs is the same as O-RU to O-DU. Therefore, different routes are added to the system to solve the routing problem. However, it provides a new system model. So, the connection between O-RUs to O-DUs is fixed and transparent. As a result, the propagation delay is fixed and does not affect the optimization problem.
The following is a brief calculation of propagation delay.
Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km. Moreover, the distance from O-CU to the network should not exceed 200 km \cite{oranD1}. so, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1ms $. Since fronhaul, midhaul, and backhaul are fiber optics, c is the speed of light. Also, due to the edge technique in O-DU or O-CU for users with low latency, this amount of latency is greatly reduced. But we also do not focus on edge processing in this paper. You can find more about these distances in this \href{https://blogs.keysight.com/blogs/inds.entry.html/2020/06/30/5g_testing_what_is-0nzj.html\%23:~:text=The\%20data\%20requirements\%20are\%20about,DUs\%20is\%20about\%2080\%20km.}{link}.
The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has a small amount.
In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 bits/sec/Hz \times BW (180 KHz)$. So the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{46 \times 180 \times 10^3} < 2 us$. As a result, the $T^{fr,t} \approx T^{mid,t} \approx T^{b,t}$. for eMBB, the packet size can be 100 times larger and the delay is not exceed the 0.6ms.

@@

We add this response in subsection II-D.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 2:} ``Also, note that for calculating processing delay requests for different services arriving at blade servers for vnf applications might get different treatment on how they access VMs or containers hence a single queue with non-priority and/or preemption (m/m/1) might not be a good approximation on the performance.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
The processing delay can be modeled as an M/M/1 queue; since the number of arrival packets in the system are from a large number of independent sources. Moreover, the impact of a single packet on the system's performance is minimal. Also, the queue discipline will be first-in first-out (FIFO), and the arrival packet is assumed to follow a Poisson process. The system's clock is constant, and the size of the tasks is not fixed. So, we suppose that service times are exponentially distributed [36]. In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services, not between UEs of one service. Because we assume that the UEs of a service have the same priority, their sent packets also have an equal priority. Also, the services are isolated, and this priority does not invalidate the queue assumption. Furthermore, one service's priority over another can be higher, affecting the whole optimization and not queue formulation since the UEs in each service have the same priority, and each service has its processing delay independent of other services.

We add this response in subsection II-D-1.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 3:} ``Also worth noting, that later on in the problem formulation there is the notion of service priority $\delta_s$ for data rate but this seems not to be used for accessing cloud resources. For example one could have changed the optimization problem and considered average allocated transmission rate and optimize with the same priorities access to cloud resources (instead of allocating equal access to vnf resources).''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
{\color{red}
In this problem, since the priority is in the objective function of the equation in (13), the priority has whole effect optimization.
So, priority is given to the whole optimization problem, and the optimization problem obtains the number of VNFs by affecting the priority term. If we were to discuss the placement of VNFs on the data centers, the problem would become a knapsack or bin-packing problem, and here the prioritization would affect the resource allocation algorithm, including memory, RAM, CPU, and bandwidth. So the algorithm was implemented based on prioritization.
}

@@

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 4:} ``Some form of rationalization should be given for abstracting Interference as Gaussian noise. This is important because we expect the system to be interference limited and cell edge users to experience significant different levels of performance compared to centre cell users.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
 $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
\begin{alignat}{4}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{alignat}
\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.

Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise. The second noise is added to the interfering signal and shown with $ I_{r,u(s,i)}^{k}$ and it is different with interference.
To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
\begin{equation}\label{eq2}
y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}{x_Q}^k_{r,u(s,i)}+ z_{u(s,i)},
\end{equation}

### 2022-03-03 Journal1/Response2/Response.tex

%\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}  $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$. Also, ${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
Moreover, ${x_P}$ denotes the precoded message before compression, and ${x_Q}$ illustrates the precoded message after compression that is shown in figure \ref{fig:pq}.
In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization Gaussian noise
($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.
\begin{figure}
  \centering
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.7]{Qdiag.png}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Precoding and Quantization of Signal}
  \label{fig:pq}
\end{figure}

We add this response in subsection II-B.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 5:} ``Constraint 13n (changed to 13k in new version) is not clear - it means that there are VMs and/or containers available in the network and an operator denies service due to an energy consumption budget (which again is not very detailed to capture the actual energy consumption of each node/vnfs under different loads etc.). In general the subsection on VNF power consumption is very limited in scope. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
{A significant issue facing the industry is reducing energy consumption. Data centers are one of the most energy-consuming parts of a network. As a result, restrictions are placed on data centers' energy, including virtual machines (VMs). So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers. So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{max}$).

@@

We add this response in subsection II-E.

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 6:} ``Some rationalization is needed on why the packet size is considered to be 20 bytes. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}

We refer to the following reference in our numerical result for this comment:

@@

\\
\hline
\end{longtable}

On [1, Page 25], the URLLC packet size is stated to be 32 bytes, and on Page 26, the packet size of mMTC is stated to be 20 bytes. We changed the URLLC packet size to 32, but it has little impact on the simulation result.

We add this reference in IV-A (reference [45]).

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 7:} ``Comparison with [18] might not be fair since that work also considers BBU capacity and also performs admission control functionalities, also there are different tenants that have different users with variable required QoS. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We use a method which is similar to the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in [18]. In this work, we have services with different QoS that contain UEs, which is similar to tenants with different QoS that is introduced in [18].
 So, we used an algorithm similar to FBDR adapted to our conditions for comparison.
Instead of BBU in C-RAN, we have O-DU and O-CU in O-RAN. To use the FBDR method, we should consider the fixed BBU capacity. We assume that O-DU and O-CU have fixed sufficient capacity in our system model. Also, our mid-haul link (F1 link) has adequate capacity, so there will be no issue using the FBDR method by separating ‌BBU to O-DU and O-CU with this assumption.
In this method, PRB and power are dynamically allocated. The number of VNFs is obtained from the simulation. The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm 1 (GAA algorithm ) for O-RU assignment.

@@

 In this section, we have a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices [37].
We need to have an algorithm to remove the inter-slice interference before solving the problem in \ref{problem}. Firstly, we should assign PRBs to slices, and in the second step, the assignment of PRBs of each slice to each UEs of a specific slice is performed. So, the assignment of PRB can be completed in two steps to remove inter-slice interference and isolate the slices. Firstly, we assign PRBs to slices. Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses Algorithm \ref{proAlg}.
Suppose $\mathcal{R}_{{s}}^{min}$ and $\mathcal{R}_{{s}}^{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
Firstly, we need to find the average PRB number used by UEs in each service. Since mMTC and URLLC transmit a short packet, each UE in mMTC and URLLC requires 1 PRB. So if slice s serves mMTC or URLLC services, with $U_s$ UEs, it requires $K_s = U_s \times 1$ PRBs. For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = Blog_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s. (eMBB slice)
So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$. $K_s^{min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.
Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$. $K_s^{max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system. Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRB in slice s (eMBB slice).
Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).
The problem can be written as follow
\begin{subequations}\label{prob:prb}
\begin{alignat}{4}
\max\limits_{\boldsymbol{\bar{K_s}}} \quad &  \sum_{s=1}^{S}\delta_s K_s \ln(\bar{K_s}) \ \\
\text{subject to} \quad  & \sum_s{\bar{K_s}} \leq K
 \label{prb0} \\
& K_s^{min} \leq \bar{K_s}  \leq K_s^{max}  \quad \forall s \in S_1,\label{prb1} \\
&  \bar{K_s} \leq K_s  \quad \forall s \in S_2, S_3,\label{prb2}
\end{alignat}
\label{constraints}
\end{subequations}
We use logarithms to assign PRBs to all slices to make
them equally fair [37]. Equation (14b) illustrates that the
sum of PRBs of slices can not exceed the maximum number
of PRBs. Equation (14c), restrict the number of PRBs
of eMBB slices and (14d), limit the number of PRBs of
URLLC and mMTC slices By relaxing $\bar{K_s}$, the objective function and constraints become convex and can be solved using the Lagrangian function.
